---
title: "Usage SNS package"
author: "Luis Benavides"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Install the package `SNS` hosted in [github](https://github.com/LuisBenavides/sns).
```{r, eval=FALSE, echo=T, results='hide'}
library("devtools")
install_github("LuisBenavides/SNS")
```

## Example 3.1.1 from Conover et al
### Using Sequential Normal Scores to Detect a Change in Location (Shewhart Scheme)
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = example82$X #get the dataset into a data frame
X.id = example82$X.id
```
Load package and get dataset from Example 8.2 \code{example82} from Qiu (Example 3.1.1 from Conover et al.)
```{r, echo=TRUE, eval=FALSE, results='hide'}
library("SNS")
X = example82$X
X.id = example82$X.id
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example82, 10))
```

Get the sns of the dataset
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id)
```
to plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(s)
```
## Example 3.2.1 from Conover et al. CUSUM Variation to Detect a Change in Location
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = example84$X #get the dataset into a data frame
X.id = example84$X.id
```
Load package and get dataset from Example 8.4 \code{example84} from Qiu (Example 3.2.1 from Conover et al.)
```{r, echo=TRUE, eval=FALSE, results='hide'}
library("SNS")
X = example84$X
X.id = example84$X.id
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example84, 10))
```

Get the sns of the dataset using a CUSUM scheme
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="CUSUM", chart.par=c(0.5, 4.389, 3)) 
```
to plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(s)
```

## Example 3.3.1 from Conover et al. EWMA Variation to Detect a Change in Location
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = example84$X #get the dataset into a data frame
X.id = example84$X.id
```
Load package and get dataset from Example 8.4 \code{example84} from Qiu (Example 3.2.1 from Conover et al.)
```{r, echo=TRUE, eval=FALSE, results='hide'}
library("SNS")
X = example84$X
X.id = example84$X.id
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example84, 10))
```

Get the sns of the dataset using a EWMA scheme
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="EWMA", chart.par=c(0.1, 2.814))
```

to plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(s)
```

## Example 3.5.1. Sequential Normal Scores with a Reference Data Set (Phase 1)
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = example87$X #get the dataset into a data frame
X.id = example87$X.id
Y = example87$Y
```
Load package and get dataset from Example 8.7 \code{example87} from Qiu (Example 3.5.1 from Conover et al.)
```{r, echo=TRUE, eval=FALSE, results='hide'}
library("SNS")
X = example87$X
X.id = example87$X.id
Y = example87$Y
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example87, 10))
```

Get the sns of the dataset using a EWMA scheme
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, Y=Y, chart="EWMA", chart.par=c(0.1, 2.814))
```

to plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(s)
```

## Example 6.1.1. Multivariate Sequential Normal Scores to Detect a Change in Location
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = cbind(example91$X1,example91$X2) #get the dataset into a data frame
X.id = example91$X.id
```

Get dataset from Example 9.1 \code{example91}.
```{r, echo=TRUE, eval=FALSE, results='hide'}
X = cbind(example91$X1,example91$X2)
X.id = example91$X.id
```

Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example91, 10))
```

Get the multivariate sequential normal scores
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
msns = MSNS(X, X.id)
```
and plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(msns)
```

## Example 6.2.1. Multivariate Sequential Normal Scores to Detect a Change in Location
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = cbind(example93$X1,example93$X2) #get the dataset into a data frame
X.id = example93$X.id
```

Get dataset from Example 9.3 \code{example93}.
```{r, echo=TRUE, eval=FALSE, results='hide'}
X = cbind(example93$X1,example93$X2)
X.id = example93$X.id
```

Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example93, 10))
```

Get the multivariate sequential normal scores
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
msns = MSNS(X, X.id)
```
and plot it
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
plot(msns)
```
