---
title: "Usage SNS package"
author: "Luis Benavides"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Install the package `SNS` hosted in [github](https://github.com/LuisBenavides/sns).
```{r, eval=FALSE, echo=T, results='hide'}
library("devtools")
install_github("LuisBenavides/SNS")
```
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = example82$X #get the dataset into a data frame
X.id = example82$X.id
```
Load package and get dataset from Example 8.2 \code{example82}.
```{r, echo=TRUE, eval=FALSE, results='hide'}
library("SNS")
X = example82$X
X.id = example82$X.id
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example82, 10))
```

## Shewhart Scheme
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id) #get the sns of the dataset
plot(s) #finally plot the sns
```

## CUSUM Scheme
Positive
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="CUSUM", chart.par=c(0.5, 2.5, 1)) #get the sns of the dataset
plot(s) #finally plot the sns
```
Negative
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="CUSUM", chart.par=c(0.5, 2.5, 2)) #get the sns of the dataset
plot(s) #finally plot the sns
```
Both
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="CUSUM", chart.par=c(0.5, 2.5, 3)) #get the sns of the dataset
plot(s) #finally plot the sns
```
## EWMA Scheme
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
s = SNS(X=X,X.id=X.id, chart="EWMA", chart.par=c(1, 1)) #get the sns of the dataset
plot(s) #finally plot the sns
```

## Multivariate SNS
```{r, echo=FALSE, eval=TRUE, results='hide',message=F, warning=F}
library("devtools")
load_all()
X = cbind(example91$X1,example91$X2) #get the dataset into a data frame
X.id = example91$X1.id
```
Table with the dataset using dataframe of \code{R} (first 10 rows).
```{r, echo=FALSE, results='asis'}
knitr::kable(head(example91, 10))
```

Get dataset from Example 9.1 \code{example91}.
```{r, echo=TRUE, eval=FALSE, results='hide'}
X = cbind(example91$X1,example91$X2)
X.id = example91$X1.id
```

Get the multivariate sequential normal scores
```{r,echo=T,eval=T, results='hide', message=F, warning=F,fig.width = 9, fig.height = 6}
msns = MSNS(X, X.id)
plot(msns)
```
